無狀態區塊鏈及運用 LRU 快取策略的評估

### 2020-07-23 abstract.tex
修正錯別字

在本論文中，我們將在基於賬號的區塊鏈上討論以下兩點：
第一，
一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
只要快取賬號的訊息，
就可以省略部分交易的證明，
以此來減少網路流量與驗證時間。
第二，
快取替換有多種策略，針對 LRU 策略，
設計了基於不可變紅黑樹與不可變值無關順序樹的兩種資料結構，
並且進行實驗比較了快取命中與快取失效的代價，
模擬現今以太坊的區塊性質，
當快取數十個區塊大小的賬戶資訊量時，
快取命中所需的查詢時間仍數倍低於梅克爾 Patricia 證明驗證的時間。

@@

In this paper, we will discuss the following two points
on account-based blockchain.
First,
it is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
there are so many ceche replacement polcies.
For LRU policies, we designed two composite data
structures which based on red-black tree and value-independent order tree.
And conduct some experiments to compare the cost of a
cache hit with the penalty of a cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.

>>>>

在本論文中，我們將在基於賬戶的區塊鏈上討論以下兩點：
第一，
一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
只要快取賬戶的訊息，
就可以省略部分交易的證明，
以此來減少網路流量與驗證時間。
第二，
快取替換有多種策略，針對 LRU 策略，
設計了基於不可變紅黑樹與不可變值無關順序樹的兩種資料結構，
並且進行實驗比較了快取命中與快取失效的代價，
模擬現今以太坊的區塊性質，
當快取數十個區塊大小的賬戶資訊量時，
快取命中所需的查詢時間仍數倍低於梅克爾 Patricia 證明驗證的時間。

@@

In this paper, we will discuss the following two points
on account-based blockchain.
First,
it is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
there are so many cache replacement policies.
For LRU policies, we designed two composite data
structures which based on red-black tree and value-independent order tree.
And conduct some experiments to compare the cost of a
cache hit with the penalty of a cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.
